Exp1 - Opt w_max and {A,phi)

### 2018-04-03 voltagebudget/analysis/paper_figures.Rmd
Update first 4 figs

mean_summary <- function(x) {
   m <- mean(x)
   return(c(y=m))
}
```

@@

# --------------------------
# INITIAL
exp <- "77"
freqs <- c(20, 30)

@@

# --------------------------
# SLOW
exp <- "79"
freqs <- c(6, 8, 10, 12, 14, 16, 18)

@@

# --------------------------
# FAST
exp <- "80"
freqs <- c(22, 24, 26, 28)#, 32, 34 ,36, 38)
for(freq in freqs){
  name <- paste("../data/exp", exp, "_d-2e-3_f", as.character(freq), ".csv", sep="")
  df <- read_csv(paste(name, sep=","))
  df %>%
    filter(n_spikes > 0) -> df

@@

# Process
fig1 %>% 
  # Add delta_spikes
  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
  # Re-norm V_osc
  mutate(V_osc = V_osc - V_osc_ref) -> fig1

# --------------------------------------------------------------------
# Summarize over As 
fig1 %>% 
  group_by(As, freq) %>% 
  summarise(
    delta_spikes = mean(delta_spikes), 
    V_b = mean(V_b), 
    V_osc = mean(V_osc), 
    V_comp = mean(V_comp), 
    V_comp_ref = mean(V_comp_ref), 
    errors = mean(errors), 
    errors_pop = mean(errors_pop), 
    variances_pop = mean(variances_pop), 
    variances = mean(variances)) -> fig2

@@

```{r, fig.width=1.5, fig.height=1.9}
fig2 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc/V_b, y=errors_pop*1e3, color=V_osc/V_b)) +
  geom_point(size=0.05, alpha=1) + 
  labs(x=expression(V[o]/V[b]), y="Avg. error (ms)") +
  lims(y=c(0, 10)) +
  scale_x_continuous(breaks=c(0, 0.5, 1.0), limits = c(0, 1)) +
  scale_color_gradient(low="lightgrey", high="red") +
  theme_classic() +
  theme(
    legend.position="none") -> p1

fig2 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc/V_b, y=variances_pop*1e3, color=V_osc/V_b)) +
  geom_point(size=0.05, alpha=1) + 
  labs(x=expression(V[o]/V[b]), y="Pop. variance (ms)") +
  scale_color_gradient(low="lightgrey", high="red") +
  scale_x_continuous(breaks=c(0, 0.5, 1.0), limits = c(0, 1)) +
  theme_classic() +
  theme(
    legend.position="none") -> p2

fig2 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=errors_pop*1e3, y=variances_pop*1e3, color=V_osc/V_b)) +
  geom_point(size=0.05, alpha=.6) +
  scale_color_gradient(low="lightgrey", high="red", name=expression(V[o]/V[b])) +
  # scale_color_gradient(low="lightgrey", high="red", name="A (namp)") +
  geom_smooth(color="black", method=lm, alpha=0.2, size=.8, linetype='dotted') +
  labs(x="Avg. error (ms)", y="Pop. variance (ms)") +
  theme_classic() +
  theme(
    legend.position="right", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p3

@@

```{r, fig.width=2.7, fig.height=2.2}
fig1 %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
  geom_point(size=0.01, alpha=0.01, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  theme_classic() +
  geom_line(data=filter(fig2, freq==20, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=errors*1e3), 
            color="black", size=0.8) +
  labs(x=expression(V[o]/V[c]), y="Error (ms)") -> p1

fig1 %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc/V_comp, y=variances*1e3)) +
  geom_point(size=0.01, alpha=0.01, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  theme_classic() +
  geom_line(data=filter(fig2, freq==20, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=variances*1e3), 
            color="black", size=0.7, alpha=1) +
  labs(x=expression(V[o]/V[c]), y="Variance (ms)") -> p2

@@

fig1 %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(freq==20) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(N %in% sample(1:max_N, 24, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
  geom_point(size=.1, alpha=0.1, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  facet_wrap(~rank, nrow=3) +
  theme_classic() + 
  scale_x_continuous(breaks=c(0, 1, 2)) +
  scale_y_continuous(breaks=c(0, 10)) +
  theme(
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),s
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) +
  labs(x=expression(V[o]/V[c]), y="Error (ms)") -> p3

@@

```{r, fig.width=3.7, fig.height=3.1}
max_N <- max(fig1$N)

fig1 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc/V_b, y=variances*1e3)) +
  geom_point(size=0.1, alpha=0.1, color="grey") + 
  theme_classic() +
  geom_line(aes(x=V_osc/V_b, y=variances_pop*1e3), 
            color="black", size=0.7, alpha=1) +
  labs(x=expression(V[o]/V[b]), y="Variance (ms)") -> p1

fig1 %>% 
  filter(freq==20) %>% 
  # filter(V_osc/V_comp <= 3) %>% 
  filter(N %in% sample(1:max_N, 10, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc/V_b, y=variances*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) + 
  facet_wrap(~rank, ncol=2) +
  geom_line(aes(x=V_osc/V_b, y=variances_pop*1e3), 
            color="black", size=0.7, alpha=1) +
  scale_colour_brewer(palette = "Accent", name="Spike count") +
  scale_x_continuous(breaks=c(0, 0.5, 1.0), limits = c(0, 1)) +
  scale_y_continuous(breaks=c(8, 12)) +
  labs(x=expression(V[o]/V[b]), y="Variance (ms)") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="none", 
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) -> p2

fig1 %>% 
  filter(freq==20) %>% 
  # filter(V_osc/V_comp <= 3) %>% 
  filter(N %in% sample(1:max_N, 5, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc/V_b, y=errors*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) + 
  facet_wrap(~rank, ncol=1) +
  geom_line(aes(x=V_osc/V_b, y=errors_pop*1e3), 
            color="black", size=0.7, alpha=1) +
  scale_colour_brewer(palette = "Accent", name="Spike count") +
  scale_x_continuous(breaks=c(0, 0.5, 1), limits = c(0, 1)) +
  scale_y_continuous(breaks=c(2, 8)) +
  labs(x=expression(V[o]/V[b]), y="Error (ms)") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="right", 
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) -> p3

# -
M = min(fig1$variances_pop)

fig1 %>% 
  filter(freq==20) %>% 
  mutate(quantile = ntile(V_osc, 10)) %>%
  filter(quantile %in% c(1, 10)) %>% 
  ggplot(aes(x=variances, fill=factor(quantile), group=quantile)) +
  geom_density(alpha=0.6, size=0.2, color="black") +
  geom_vline(xintercept = M, color="black") +
  labs(x="Variance (ms)", y="Density (AU)") +
  scale_fill_manual(
    # values=c("#FFDED3", "#FD0D11"), 
    values=c("grey", "black"),
    name=expression("Deciles V"[o]), 
    labels=c("0 - 10%", "90 - 100%")) +
  theme_classic() +
  theme(
    legend.position="bottom", 
    legend.key.size = unit(.3, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8) ) -> p4

fig1 %>% 
  filter(freq==20) %>% 
  ggplot(aes(x=delta_spikes, y=variances*1e3, color=factor(delta_spikes))) +
  geom_boxplot(outlier.size = NA, size=0.8, show.legend=FALSE)+
  labs(x="Spike count", y="Variance (ms)") +
  scale_colour_brewer(palette = "Accent", name="Spike count") +
  theme_classic() +
  theme(legend.position="none") -> p5

fig1 %>% 
  filter(freq==20) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  ggplot(aes(y=V_osc/V_comp, x=delta_spikes)) +
  geom_jitter(size=0.1, alpha=0.01) + 
  geom_hline(yintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_hline(yintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  theme_classic() +
  labs(y=expression(V[o]/V[c]), x="Spike count") -> p6

plot_grid <- rbind(
  c(1,  1,  1,  1,  2,  2,  2, 2, 3, 3,  3, 3),
  c(1,  1,  1,  1,  2,  2,  2, 2, 3, 3,  3, 3),
  c(1,  1,  1,  1,  2,  2,  2, 2, 3, 3,  3, 3),
  c(4,  4,  4,  4,  2,  2,  2, 2, 3, 3,  3, 3),
  c(4,  4,  4,  4,  2,  2,  2, 2, 3, 3,  3, 3),
  c(4,  4,  4,  4,  2,  2,  2, 2, 3, 3,  3, 3),
  c(NA, NA, NA, NA, NA, NA, 5, 5, 5, 6,  6, 6),
  c(NA, NA, NA, NA, NA, NA, 5, 5, 5, 6,  6, 6),
  c(NA, NA, NA, NA, NA, NA, 5, 5, 5, 6,  6, 6))

>>>>

mean_summary <- function(x) {
   m <- mean(x)
   return(c(y=m))
}
sample_n_groups = function(tbl, size, replace = FALSE, weight = NULL) {
  # regroup when done
  grps = tbl %>% groups %>% lapply(as.character) %>% unlist
  # check length of groups non-zero
  keep = tbl %>% summarise() %>% ungroup() %>% sample_n(size, replace, weight)
  # keep only selected groups, regroup because joins change count.
  # regrouping may be unnecessary but joins do something funky to grouping variable
  tbl %>% right_join(keep, by=grps) %>% group_by_(.dots = grps)
}
```

@@

# --------------------------
# INITIAL
exp <- "96"
freqs <- c(20, 30)

@@

# --------------------------
# SLOW
exp <- "94"
freqs <- c(6, 8, 10, 12, 14, 16, 18)

@@

# --------------------------
# FAST
exp <- "95"
freqs <- c(22, 24, 26, 28)#, 32, 34 ,36, 38)
for(freq in freqs){
  name <- paste("../data/exp", exp, "_d-2e-3_f", as.character(freq), ".csv", sep="")
  df <- read_csv(paste(name, sep=","))
  df %>%
    filter(n_spikes > 0) -> df

@@

# Process
fig1 %>% 
  filter(n_spikes_ref > 0) %>% 
  # Add delta_spikes
  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
  # Re-norm V_osc
  mutate(V_osc = V_osc - V_osc_ref) -> fig1

# --------------------------------------------------------------------
# Summarize over As 
fig1 %>% 
  group_by(As, freq) %>% 
  summarise(
    N = 0,
    delta_spikes = mean(delta_spikes), 
    V_b = mean(V_b), 
    V_osc = mean(V_osc), 
    V_comp = mean(V_comp), 
    V_comp_ref = mean(V_comp_ref), 
    errors = mean(errors), 
    errors_pop = mean(errors_pop), 
    variances_pop = mean(variances_pop), 
    variances = mean(variances)) -> fig2

@@

```{r, fig.width=1.5, fig.height=1.9}
fig2 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc/V_b, y=errors_pop*1e3, color=V_osc/V_b)) +
  geom_point(size=0.05, alpha=1) + 
  labs(x=expression(V[o]/V[b]), y="Avg. error (ms)") +
  # lims(y=c(0, 10)) +
  scale_x_continuous(breaks=c(0, 0.5, 1.0), limits = c(0, 1)) +
  scale_color_gradient(low="darkgrey", high="red") +
  theme_classic() +
  theme(
    legend.position="none") -> p1

fig2 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc/V_b, y=variances_pop*1e3, color=V_osc/V_b)) +
  geom_point(size=0.05, alpha=1) + 
  labs(x=expression(V[o]/V[b]), y="Pop. variance (ms)") +
  scale_color_gradient(low="darkgrey", high="red") +
  scale_x_continuous(breaks=c(0, 0.5, 1.0), limits = c(0, 1)) +
  theme_classic() +
  theme(
    legend.position="none") -> p2

fig2 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=errors_pop*1e3, y=variances_pop*1e3, color=V_osc/V_b)) +
  geom_point(size=0.05, alpha=.6) +
  scale_color_gradient(low="darkgrey", high="red", name=expression(V[o]/V[b])) +
  # scale_color_gradient(low="darkgrey", high="red", name="A (namp)") +
  geom_smooth(color="red", method=lm, alpha=0.2, size=.15, se=FALSE, linetype='solid') +
  labs(x="Avg. error (ms)", y="Pop. variance (ms)") +
  theme_classic() +
  theme(
    legend.position="right", 
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p3

@@

```{r, fig.width=2.7, fig.height=2.2}
fig1 %>% 
  group_by(N) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(freq == 20) %>% 
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3, group=N)) +
  geom_line(size=0.5, alpha=0.2, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  theme_classic() +
  geom_line(data=filter(fig2, freq==20, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=errors*1e3), 
            color="black", size=0.8) +
  labs(x=expression(V[o]/V[c]), y="Error (ms)") -> p1

fig1 %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(freq == 20) %>% 
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  ggplot(aes(x=V_osc/V_comp, y=variances*1e3, group=N)) +
  geom_line(size=0.5, alpha=0.2, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  theme_classic() +
  geom_line(data=filter(fig1, freq==20, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=variances_pop*1e3), 
            color="black", size=0.7, alpha=1) +
  labs(x=expression(V[o]/V[c]), y="Variance (ms)") -> p2

@@

fig1 %>% 
  filter(freq==20) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(N %in% sample(1:max_N, 24, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3, group=N)) +
  geom_line(size=.5, alpha=0.9, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  facet_wrap(~rank, nrow=3) +
  theme_classic() + 
  scale_x_continuous(breaks=c(0, 1, 2)) +
  scale_y_continuous(breaks=c(0, 10)) +
  theme(
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),s
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) +
  labs(x=expression(V[o]/V[c]), y="Error (ms)") -> p3

@@

```{r, fig.width=2.6, fig.height=3.2}
max_N <- max(fig1$N)

fig1 %>% 
  filter(freq == 20) %>% 
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  ggplot(aes(x=V_osc/V_b, y=variances*1e3, group=N)) +
  geom_line(size=0.5, alpha=0.2, color="grey") + 
  theme_classic() +
  geom_line(aes(x=V_osc/V_b, y=variances_pop*1e3), 
            color="black", size=0.7, alpha=1) +
  labs(x=expression(V[o]/V[b]), y="Variance (ms)") -> p1

fig1 %>% 
  filter(freq == 20) %>% 
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  ggplot(aes(x=V_osc/V_b, y=variances*1e3, group=N, color=factor(delta_spikes))) +
  geom_line(size=0.4, alpha=0.6) + 
  scale_colour_brewer(
    palette = "Reds", guide=guide_legend(title="Spike count", nrow=3)) +
  labs(x=expression(V[o]/V[b]), y="Variance (ms)") +
  theme_classic() + theme(legend.position="none") -> p2

# -
M = min(fig1$variances_pop)
fig1 %>% 
  filter(freq == 20) %>% 
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  ggplot(aes(x=variances*1e3, fill=factor(delta_spikes))) +
  geom_density(alpha=0.6, size=0, color="black") +
  scale_fill_brewer(palette = "Reds", name="Spike\ncount") +
  geom_vline(xintercept = M*1e3, color="black", linetype="dotted") +
  labs(x="Variance (ms)", y="Density (AU)") +
  theme_classic() + 
  theme(legend.position = c(1.25, 1.55), 
        legend.background = element_rect(colour ="black"),
        legend.key.size = unit(.5, "cm"),
        legend.title = element_text(size=10),
        legend.text = element_text(size=10)) -> p3

fig1 %>% 
  filter(freq==20) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  ggplot(aes(y=V_osc/V_comp, x=factor(delta_spikes), group=delta_spikes)) +
  geom_jitter(aes(color=factor(delta_spikes)), size=0.01, alpha=0.1, width=0.2) +
  geom_boxplot(outlier.colour = NA, alpha=0.9, width=0.2) +
  scale_colour_brewer(palette = "Reds", name="Spike count") +
  geom_hline(yintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_hline(yintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  theme_classic() +
  theme(legend.position = "none") +
  labs(y=expression(V[o]/V[c]), x="Spike count") + 
  coord_flip()  -> p4

fig1 %>%
  filter(freq==20) %>%
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  ungroup() %>% 
  group_by(N) %>% 
  sample_n_groups(8) %>% 
  ggplot(aes(x=V_osc/V_b, y=variances*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) +
  facet_wrap(~N, nrow=8) +
  geom_line(aes(x=V_osc/V_b, y=variances_pop*1e3),
            color="black", size=0.7, alpha=1) +
  scale_colour_brewer(palette = "Reds", name="Spike count") +
  scale_x_continuous(breaks=c(0, 0.5, 1.0), limits = c(0, 1)) +
  scale_y_continuous(breaks=c(6, 12)) +
  labs(x=expression(V[o]/V[b]), y="Variance (ms)") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="none",
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) -> p5

fig1 %>%
  filter(freq==20) %>%
  filter(V_osc/V_comp <= 3) %>%
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  sample_n_groups(8) %>% 
  ggplot(aes(x=V_osc/V_b, y=errors*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) +
  facet_wrap(~N, nrow=8) +
  # geom_line(aes(x=V_osc/V_b, y=errors_pop*1e3),
  #           color="black", size=0.7, alpha=1) +
  scale_colour_brewer(palette = "Reds", name="Spike count") +
  scale_x_continuous(breaks=c(0, 0.5, 1), limits = c(0, 1)) +
  scale_y_continuous(breaks=c(2, 8)) +
  labs(x=expression(V[o]/V[b]), y="Error (ms)") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="none",
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) -> p6

plot_grid <- rbind(
  c(1, 1, 1, NA, 5, 5, 6, 6),
  c(1, 1, 1, NA, 5, 5, 6, 6),
  c(1, 1, 1, NA, 5, 5, 6, 6),
  c(2, 2, 2, NA, 5, 5, 6, 6),
  c(2, 2, 2, NA, 5, 5, 6, 6),
  c(2, 2, 2, NA, 5, 5, 6, 6),
  c(3, 3, 3, NA, 5, 5, 6, 6),
  c(3, 3, 3, NA, 5, 5, 6, 6),
  c(3, 3, 3, NA, 5, 5, 6, 6),
  c(4, 4, 4, NA, NA, NA, NA, NA),
  c(4, 4, 4, NA, NA, NA, NA, NA),
  c(4, 4, 4, NA, NA, NA, NA, NA))
